Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-08 paper/manuscript.tex
edits to legends for H3 vs H1

\begin{figure*}
\centering
\includegraphics[width=15cm]{figs/WSN_trunkvssidebranch/WSN_trunkvssidebranch.pdf}
\caption{\label{fig:WSN_trunkvssidebranch}
{\bf The WSN/1933 H1 preferences do not reveal differences in trunk vs side branch mutational effects}
(A) We used the WSN/1933 H1 preferences experimentally measured in~\cite{doud2016accurate} to calculate the log$_{2}$ mutational effects of trunk and side branch mutations from the inferred H3N2 phylogeny in Figure~\ref{fig:trunkvssidebranch}.
(B) We also performed a sliding window analysis with the WSN/1933 H1 preferences.
}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=17cm]{figs/distance_distribution/distance_distribution.pdf}
\caption{\label{fig:distance_distribution}
{\bf The HA homologs exhibit many large shifts in preference compared to shifts for other viral protein homologs}
(A) A phylogenetic tree of the HA subtypes, with the two HA's, WSN/1933 H1 and Perth/2009 H3, for which we have measured amino-acid preferences denoted on the tree. 
The WSN/1933 H1 and the Perth/2009 H3 share $\sim$42\% amino-acid identity.
(B) The correlations of the amino-acid preferences for replicates both within and between the two HA homologs. 
The within-Perth/2009 and the within-WSN/1933 correlations are shown in purple and brown, respectively.
The between homolog correlations are in gray.
(C) The distribution of shifts in preference for various homolog pairs are shown.
The top two distributions show the distances between each of the HA homologs with the non-homologous HIV Env~\cite{haddox2017mapping}. %BF520
The center distribution shows the corrected distance between the two HIV Env homologs, which share 86\% amino-acid identity.
The fourth distribution from the top is a null generated by randomizing the HA replicates and computing the distances.
The bottom distribution is the corrected distance between the Perth/2009 H3 and WSN/1933 H1 homologs at all sites that align.
}
\end{figure*}

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figs/WSN_trunkvssidebranch/WSN_trunkvssidebranch.pdf}
\caption{\label{fig:WSN_trunkvssidebranch}
{\bf Experimental measurements on an H1 HA do \emph{not} provide evolutionarily relevant information for H3 HAs.}
(A), (B) This figure is analogous to that in Figure~\ref{fig:trunkvssidebranch} except that it scores the H3 sequences using experimental measurements made on the lab-adapted WSN/1933 HA~\cite{doud2016accurate}.
\comment{Make into two vertical panels}
}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=17cm]{figs/distance_distribution/distance_distribution.pdf}
\caption{\label{fig:distance_distribution}
{\bf There are substantial differences in the effects of mutations between H1 and H3 HAs.}
(A) Phylogenetic tree of HA subtypes, with the WSN/1933 H1 and Perth/2009 H3 HAs labeled. 
These HAs have $\sim$42\% amino-acid identity\comment{get the exact number rounded the percent and remove the $\sim$ symbol}.
(B) All pairwise correlations of the amino-acid preferences measured in the three individual deep mutational scanning replicates in the current study  and the three replicates in prior deep mutational scanning of an H1 HA~\cite{doud2016accurate}.
Comparisons between H3 replicates are in purple, those between H1 replicates are in brown, and those across H1 and H3 replicates are in gray. 
$R$ indicates the Pearson correlation coefficient.
(C) We calculated the shift in amino-acid preferences at each site between H3 and H1 HAs using the method in \cite{haddox2017mapping}, and plotted the distribution of shifts for all sites.
The shifts between H3 and H1 (yellow) are much larger than the null distribution (blue) expected if all differences to experimental noise.
The shifts are also much larger than those previously observed between two variants of HIV envelope protein (Env) that share 86\% amino-acid identity (pink).
However, the shifts between H3 and H1 are still less than the differences between either HA and HIV Env (green).
\comment{Let's remove RMSDcorrected from legend.}
}
\end{figure*}
